---
title: "QTL Mapping of ERA8"
output:
  html_document:
    code_download: yes
    code_folding: "show" 
    toc: true
    toc_depth: 5
    toc_float: true
    theme: flatly
  pdf_document: default
date: "`r format(Sys.time(), '%Y.%m.%d')`"
---

**Title**: Exome sequencing of bulked segregants identified a novel *TaMKK3-A* allele linked to the wheat *ERA8* ABA-hypersensitive germination phenotype

**Authors**: Shantel A. Martinez, Oluwayesi Shorinola, Samantha Conselman, Deven See, Daniel Z. Skinner, Cristobal Uauy, and Camille M. Steber

This document contains all datasets on which the conclusions of the paper, Martinez et al. 2020, to enable reproducibility of the QTL Mapping. 

The datasets generated during and/or analysed during the current study are available in the GitHub repository, [github.com/shantel-martinez/ERA8-Mapping](github.com/shantel-martinez/ERA8-Mapping).  

#### Load All Data
To download all of the datasets used in this analysis: 
```{r echo=FALSE}
setDownloadURI = function(list, filename = stop("'filename' must be specified"), textHTML = "", fileext = "RData", envir = parent.frame()){
  require(base64enc,quietly = TRUE)
  divname = paste(sample(LETTERS),collapse="")
  tf = tempfile(pattern=filename, fileext = fileext)
  save(list = list, file = tf, envir = envir)
  filenameWithExt = paste(filename,fileext,sep=".")
  
  uri = dataURI(file = tf, mime = "application/octet-stream", encoding = "base64")
  cat("<a style='text-decoration: none' id='",divname,"'></a>
    <script>
    var a = document.createElement('a');
    var div = document.getElementById('",divname,"');
    div.appendChild(a);
    a.setAttribute('href', '",uri,"');
    a.innerHTML = '",textHTML,"' + ' (",filenameWithExt,")';
    if (typeof a.download != 'undefined') {
      a.setAttribute('download', '",filenameWithExt,"');
    }else{
      a.setAttribute('onclick', 'confirm(\"Your browser does not support the download HTML5 attribute. You must rename the file to ",filenameWithExt," after downloading it (or use Chrome/Firefox/Opera). \")');
    }
    </script>",
    sep="")
}
e <- load("./ERA8-Mapping-Data.RData")
```

```{r results='asis',echo=FALSE,message=FALSE}
setDownloadURI("e", filename = "ERA8-Mapping-Data")
```
</br> 
Once downloaded, the environment can be loaded:  
```{r eval = FALSE}
load("./ERA8-Mapping-Data.RData")
```

#### Load Libraries
```{r warning=FALSE, message=FALSE}
library(qtl)
library(ggplot2) 
font<-element_text(face = "bold",  size = 16) #ggplot preference
library(tidyverse)
library(kableExtra)
library(knitr)
library(DT)
```

## Zak/ZakERA8 BC3F2:3
The `ZZ8` dataset contains Zak/ZakERA8 BC3 F2:3 genotypic data, phenotypic data, and marker positions on chromosome 4A.    
```{r eval=FALSE}
ZZ8 <- read.cross("csv",".","./ZZ8_SNP1-SNP_30_all.csv",na.strings=c("-","NA","."),BC.gen=3, F.gen=2)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
# ZZ8 <- read.cross("csv",".","./ZZ8_SNP1-SNP_30_all.csv",na.strings=c("-","NA","."),BC.gen=3, F.gen=2)
ZZ8
```
Phenotypes include: Percent Germination (`PG`) and Germination Index (`GI`)  

#### Composite Interval Mapping 
```{r}
data_2 <- calc.genoprob(ZZ8, step=0)
out.cimPGavg <- cim(data_2, pheno.col="PG",map.function=c("kosambi"),method=c("hk"))
out.cimPGavg$Trait <- ("PG") 
out.cimGIavg <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
out.cimGIavg$Trait <- ("GI")
```

#### Determine Significance Threshhold  
```{r eval = FALSE}
a <- scanone(ZZ8, method="hk", pheno.col = "PG", n.perm=1000)
b <- scanone(ZZ8, method="hk", pheno.col = "GI", n.perm=1000)
summary(a) 
summary(b)
```

#### Wrangle Results  
```{r}
ZZ8_all <- rbind(out.cimPGavg, out.cimGIavg)
ZZ8_all$Population <- ("all")
```

***   
**Repeat CIM for the X5.1 subset only**   
```{r eval = FALSE}
data5.1<-read.cross("csv",".","./ZZ8_SNP1-SNP_30_5.1.csv",na.strings=c("-","NA","."),BC.gen=3, F.gen=2)
```
```{r  echo = FALSE}
data5.1
```

```{r eval = FALSE}
data_2 <- calc.genoprob(data5.1, step=0)
out.cimPGavg <- cim(data_2, pheno.col="PG",map.function=c("kosambi"),method=c("hk"))
out.cimPGavg$Trait <- ("PG") 
out.cimGIavg <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
a <- scanone(data5.1, method="hk", pheno.col = "PG", n.perm=1000)
b <- scanone(data5.1, method="hk", pheno.col = "GI", n.perm=1000)
summary(a) 
summary(b) 
ZZ8_5.1 <- rbind(out.cimPGavg, out.cimGIavg)
ZZ8_5.1$Population <- ("5.1")
```
```{r echo = FALSE}
data_2 <- calc.genoprob(data5.1, step=0)
out.cimPGavg <- cim(data_2, pheno.col="PG",map.function=c("kosambi"),method=c("hk"))
out.cimPGavg$Trait <- ("PG") 
out.cimGIavg <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
out.cimGIavg$Trait <- ("GI")
ZZ8_5.1 <- rbind(out.cimPGavg, out.cimGIavg)
ZZ8_5.1$Population <- ("5.1")
```


***  
**Repeat CIM for the X5.2a subset only**   
```{r eval = FALSE}
data5.2a<-read.cross("csv",".","./ZZ8_SNP1-SNP_30_5.2a.csv",na.strings=c("-","NA","."),BC.gen=3, F.gen=2)
```
```{r  echo = FALSE}
data5.2a
```


```{r  eval = FALSE}
data_2 <- calc.genoprob(data5.2a, step=0)
out.cimPGavg <- cim(data_2, pheno.col="PG",map.function=c("kosambi"),method=c("hk"))
out.cimPGavg$Trait <- ("PG") 
out.cimGIavg <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
out.cimGIavg$Trait <- ("GI")
a <- scanone(data5.2a, method="hk", pheno.col = "PG", n.perm=1000)
b <- scanone(data5.2a, method="hk", pheno.col = "GI", n.perm=1000)
summary(a) 
summary(b) 
ZZ8_5.2a <- rbind(out.cimPGavg, out.cimGIavg)
ZZ8_5.2a$Population <- ("5.2a")
```

```{r echo = FALSE}
data_2 <- calc.genoprob(data5.2a, step=0)
out.cimPGavg <- cim(data_2, pheno.col="PG",map.function=c("kosambi"),method=c("hk"))
out.cimPGavg$Trait <- ("PG") 
out.cimGIavg <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
out.cimGIavg$Trait <- ("GI")
ZZ8_5.2a <- rbind(out.cimPGavg, out.cimGIavg)
ZZ8_5.2a$Population <- ("5.2a")
```

**Repeat CIM for the X5.2b subset only**   

```{r eval = FALSE}
data5.2b <- read.cross("csv",".","./ZZ8_SNP1-SNP_30_5.2b.csv",na.strings=c("-","NA","."),BC.gen=3, F.gen=2)
```
```{r  echo = FALSE}
data5.2b
```

```{r eval = FALSE}
data_2 <- calc.genoprob(data5.2b, step=0)
out.cimPGavg <- cim(data_2, pheno.col="PG",map.function=c("kosambi"),method=c("hk"))
out.cimPGavg$Trait <- ("PG") 
out.cimGIavg <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
out.cimGIavg$Trait <- ("GI")
a <- scanone(data5.2b, method="hk", pheno.col = "PG", n.perm=1000)
b <- scanone(data5.2b, method="hk", pheno.col = "GI", n.perm=1000)
summary(a) 
summary(b) 
ZZ8_5.2b <- rbind(out.cimPGavg, out.cimGIavg)
ZZ8_5.2b$Population <- ("5.2b")
```
```{r echo = FALSE}
data_2 <- calc.genoprob(data5.2b, step=0)
out.cimPGavg <- cim(data_2, pheno.col="PG",map.function=c("kosambi"),method=c("hk"))
out.cimPGavg$Trait <- ("PG") 
out.cimGIavg <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
out.cimGIavg$Trait <- ("GI")
ZZ8_5.2b <- rbind(out.cimPGavg, out.cimGIavg)
ZZ8_5.2b$Population <- ("5.2b")
```

#### Graph Results
QTL Graph for Germination Index (`GI`)  
```{r eval=FALSE}
ZZ8_QTL <- rbind(ZZ8_all, ZZ8_5.1, ZZ8_5.2b, ZZ8_5.2a)
GI <- ZZ8_QTL[(ZZ8_QTL$Trait %in% "GI"),]

ggplot(data = GI , aes(x=GI$pos, y=GI$lod)) + 
  geom_line(aes(colour=GI$Population), size=1)+geom_hline(aes(yintercept = 1.85))+
  theme_bw()+ theme(axis.text = font,  axis.title = font)+ 
  labs(x = "Chromosome 4A ERA8 Region (cM)", y = "LOD")+
  scale_color_manual(values=c("#78c679", "#006837", "#31a354","#A2CD5A")) #+ theme(legend.position="none") +
  # ggsave("ZZ8_4A_QTL.png", width = 3, height = 3, units = "in")
```
## Fig 3a
```{r  echo=FALSE}
ZZ8_QTL <- rbind(ZZ8_all, ZZ8_5.1, ZZ8_5.2b, ZZ8_5.2a)
GI <- ZZ8_QTL[(ZZ8_QTL$Trait %in% "GI"),]

ggplot(data = GI , aes(x=GI$pos, y=GI$lod)) + 
  geom_line(aes(colour=GI$Population), size=1)+geom_hline(aes(yintercept = 1.85))+
  theme_bw()+ theme(axis.text = font,  axis.title = font)+ 
  labs(x = "Chromosome 4A ERA8 Region (cM)", y = "LOD")+
  scale_color_manual(values=c("#78c679", "#006837", "#31a354","#A2CD5A")) #+ theme(legend.position="none") +
  # ggsave("ZZ8_4A_QTL.png", width = 3, height = 3, units = "in")
```

## Louise/ZakERA8 RIL F6:7 
### EMS-derived SNPs 
```{r  warning=FALSE, message=FALSE}
# LZ8 <- read.cross("csv",".","./LZ8_SNP1-SNP30_MKK3.csv",na.strings=c("-","NA","."),BC.gen=0, F.gen=5)
LZ8
```


```{r}
data_2 <- calc.genoprob(data5.2b, step=0)
data_2 <- calc.genoprob(LZ8, step=0)

out.cimE1PGD1 <- cim(data_2, pheno.col="E1D1",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD1$Trait <- ("E1PGD1") 
out.cimE1PGD2 <- cim(data_2, pheno.col="E1D2",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD2$Trait <- ("E1PGD2")
out.cimE1PGD3 <- cim(data_2, pheno.col="E1D3",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD3$Trait <- ("E1PGD3")
out.cimE1PGD4 <- cim(data_2, pheno.col="E1D4",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD4$Trait <- ("E1PGD4")
out.cimE1PGD5 <- cim(data_2, pheno.col="E1D5",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD5$Trait <- ("E1PGD5")
out.cimE1GIavg <- cim(data_2, pheno.col="E1GI",map.function=c("kosambi"),method=c("hk"))
out.cimE1GIavg$Trait <- ("E1GIavg")

out.cimE2PGD1 <- cim(data_2, pheno.col="E2D1",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD1$Trait <- ("E2PGD1")
out.cimE2PGD2 <- cim(data_2, pheno.col="E2D2",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD2$Trait <- ("E2PGD2")
out.cimE2PGD3 <- cim(data_2, pheno.col="E2D3",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD3$Trait <- ("E2PGD3")
out.cimE2PGD4 <- cim(data_2, pheno.col="E2D4",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD4$Trait <- ("E2PGD4")
out.cimE2PGD5 <- cim(data_2, pheno.col="E2D5",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD5$Trait <- ("E2PGD5")
out.cimE2GIavg <- cim(data_2, pheno.col="E2GI",map.function=c("kosambi"),method=c("hk"))
out.cimE2GIavg$Trait <- ("E2GIavg")

out.cimE3PGD1 <- cim(data_2, pheno.col="E3D1",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD1$Trait <- ("E3PGD1")
out.cimE3PGD2 <- cim(data_2, pheno.col="E3D2",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD2$Trait <- ("E3PGD2")
out.cimE3PGD3 <- cim(data_2, pheno.col="E3D3",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD3$Trait <- ("E3PGD3")
out.cimE3PGD4 <- cim(data_2, pheno.col="E3D4",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD4$Trait <- ("E3PGD4")
out.cimE3PGD5 <- cim(data_2, pheno.col="E3D5",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD5$Trait <- ("E3PGD5")
out.cimE3GIavg <- cim(data_2, pheno.col="E3GI",map.function=c("kosambi"),method=c("hk"))
out.cimE3GIavg$Trait <- ("E3GIavg")

QTL.LZ8.ERA8 <- rbind(out.cimE1PGD1, out.cimE1PGD2, out.cimE1PGD3, out.cimE1PGD4, out.cimE1PGD5, 
                      out.cimE1GIavg, out.cimE2PGD1, out.cimE2PGD2, out.cimE2PGD3, out.cimE2PGD4, 
                      out.cimE2PGD5, out.cimE2GIavg,out.cimE3PGD1, out.cimE3PGD2, out.cimE3PGD3, 
                      out.cimE3PGD4, out.cimE3PGD5, out.cimE3GIavg)
QTL.LZ8.Day1 <- rbind(out.cimE1PGD1, out.cimE2PGD1,out.cimE3PGD1)
QTL.LZ8.GI <- rbind(out.cimE1GIavg, out.cimE2GIavg,out.cimE3GIavg)
```

Calculating the significant LOD score threshold for each trait
```{r eval=FALSE, warning=FALSE, message=FALSE}
a<-scanone(LZ8, method="hk", pheno.col = "E1D1", n.perm=1000)
c<-scanone(LZ8, method="hk", pheno.col = "E1D2", n.perm=1000)
d<-scanone(LZ8, method="hk", pheno.col = "E1D3", n.perm=1000)
e<-scanone(LZ8, method="hk", pheno.col = "E1D4", n.perm=1000)
f<-scanone(LZ8, method="hk", pheno.col = "E1D5", n.perm=1000)
g<-scanone(LZ8, method="hk", pheno.col = "E1GI", n.perm=1000)
b1<-scanone(LZ8, method="hk", pheno.col = "E2D1", n.perm=1000)
c1<-scanone(LZ8, method="hk", pheno.col = "E2D2", n.perm=1000)
d1<-scanone(LZ8, method="hk", pheno.col = "E2D3", n.perm=1000)
e1<-scanone(LZ8, method="hk", pheno.col = "E2D4", n.perm=1000)
f1<-scanone(LZ8, method="hk", pheno.col = "E2D5", n.perm=1000)
g1<-scanone(LZ8, method="hk", pheno.col = "E2GI", n.perm=1000)
h<-scanone(LZ8, method="hk", pheno.col = "E3D1", n.perm=1000)
i<-scanone(LZ8, method="hk", pheno.col = "E3D2", n.perm=1000)
j<-scanone(LZ8, method="hk", pheno.col = "E3D3", n.perm=1000)
k<-scanone(LZ8, method="hk", pheno.col = "E3D4", n.perm=1000)
l<-scanone(LZ8, method="hk", pheno.col = "E3D5", n.perm=1000)
m<-scanone(LZ8, method="hk", pheno.col = "E3GI", n.perm=1000)
summary(a) #2.12 E1D1 
summary(c) #2.10
summary(d) #2.20
summary(e) #2.15
summary(f) #2.02
summary(g) #1.98
summary(b1) #2.06 E2D1
summary(c1) #2.17
summary(d1) #2.03
summary(e1) #1.96
summary(f1) #2.17
summary(g1) #2.10
summary(h) #2.01 E3D1
summary(i) #2.01
summary(j) #2.21
summary(k) #2.12
summary(l) #2.11
summary(m) #2.19
```


QTL Graph for GI
```{r warning=FALSE, message=FALSE}
ggplot(QTL.LZ8.GI, aes(x=QTL.LZ8.GI$pos, y=QTL.LZ8.GI$lod))+
  geom_line(aes(colour = factor(Trait)),size = 1)+
  theme_bw()+ theme(axis.text = font,  axis.title = font)+
  geom_hline(aes(yintercept = 2.10))+ 
  labs(x = "Chromosome 4A (cM)", y = NULL) +
  ylim (0,10) +
  scale_color_manual(values=c("#96CDCD", "#20B2AA", "#00868B")) #+ theme(legend.position="none") #+ 
  # ggsave("LZ8_4A_QTL.png", width = 3, height = 3, units = "in")
```

### Genotyping-by-sequencing SNPs

```{r warning=FALSE, message=FALSE}
# LZ8GBS <- read.cross("csv",".","./LZ8_GBS_all.csv",na.strings=c("-","NA","."),BC.gen=0, F.gen=5)
LZ8GBS
```

View genotypic data
```{r}
plot.map(LZ8GBS)
geno.image(LZ8GBS)
```

Omit Skewed Markers with potential segregation distortion
```{r}
gt<-geno.table(LZ8GBS)
g <- gt[gt$P.value<0.05/totmar(LZ8GBS),]
datatable(g)
```

```{r}
drop <- c( "A15328_3A_7A_70" ,"A23596_unk_70" ,"A1484_unk_70" ,"A13016_1B_70" ,"A15940_1B_100" ,"A9591_1B_100" ,"A576_1B_70" ,"A18104_1D_100" ,"A27014_1B_2B_100","A17967_2D_100" ,"A13978_2D_70" ,"A25742_3A_100" ,"A18332_3A_70" ,"A12777_3D_100" ,"A273_4A_100" ,"A21245_4A_70" ,"A10491_4A_70" ,"A18377_4A_4B_70" ,"A25000_4B_70" ,"A25441_4B_100" ,"A4035_4D_100" ,"A18379_4D_100" ,"A18009_4D_70" ,"A19099_4D_7D_100","A16328_4D_70" ,"A11848_4D_70" ,"A12209_4D_100" ,"A27652_4D_100" ,"A21275_5A_100" ,"A25877_5A_100" ,"A25439_5A_70" ,"A25438_unk_70" ,"A20969_5A_70" ,"A8097_5A_100" ,"A19723_5A_100" ,"A11602_5A_100" ,"A7781_5A_100" ,"A11185_5D_100" ,"A27769_5D_100" ,"A16263_3D_5D_100","A18607_5D_100" ,"A25725_5D_100" ,"A1900_6A_70" ,"A11910_3A_6A_70" ,"A25264_6A_70" ,"A20866_6A_100" ,"A11585_6B_70" ,"A11967_6B_100" ,"A20255_6B_100" ,"A19959_6B_70" ,"A27878_6B_70" ,"A28179_6B_100" ,"A28536_6B_70" ,"A1460_6B_100" ,"A9811_6B_100" ,"A16328_6B_100" ,"A13442_6B_70" ,"A26650_3A_4B_70" ,"A8101_6B_100" ,"A7718_6B_6D_70" ,"A10138_6B_70" ,"A27566_unk_70" ,"A15195_unk_70" ,"A15639_unk_100" ,"A10596_6B_100" ,"A27867_unk_100" ,"A10599_unk_100" ,"A20619_6B_100" ,"A7070_6B_100" ,"A6713_1B_6B_70" ,"A22215_6B_100" ,"A499_5D_100" ,"A21788_6D_70" ,"A21995_6D_100" ,"A18389_6D_100" ,"A11691_6D_100" ,"A11316_6D_70" ,"A28649_6D_70" ,"A28881_6D_100" ,"A18071_6D_100" ,"A8016_7A_7D_100" ,"A6637_unk_70" ,"A7471_7A_100" ,"A12324_4B_7B_70" ,"A13388_7B_100" ,"A28147_7B_100" ,"A27851_7B_70" ,"A11842_7D_70" ,"A28228_7D_100" ,"A21486_7D_100" ,"A27928_7D_70" ,"A18989_unk_100","A7100_7A_70","A23150_unk_70")
LZ8GBS <- drop.markers(LZ8GBS, drop)
gt<-geno.table(LZ8GBS)
gt[gt$P.value<0.05/totmar(LZ8GBS),]
```

#### Composite Interval Mapping
Across all traits  
```{r warning=FALSE, message=FALSE}
data_2 <- calc.genoprob(LZ8GBS, step=0)
out.cimE1PGD1 <- cim(data_2, pheno.col="E1D1",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD1$Trait <- ("E1PGD1") 
out.cimE1PGD2 <- cim(data_2, pheno.col="E1D2",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD2$Trait <- ("E1PGD2")
out.cimE1PGD3 <- cim(data_2, pheno.col="E1D3",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD3$Trait <- ("E1PGD3")
out.cimE1PGD4 <- cim(data_2, pheno.col="E1D4",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD4$Trait <- ("E1PGD4")
out.cimE1PGD5 <- cim(data_2, pheno.col="E1D5",map.function=c("kosambi"),method=c("hk"))
out.cimE1PGD5$Trait <- ("E1PGD5")
out.cimE1GIavg <- cim(data_2, pheno.col="E1GI",map.function=c("kosambi"),method=c("hk"))
out.cimE1GIavg$Trait <- ("E1GIavg")
out.cimE2PGD1 <- cim(data_2, pheno.col="E2D1",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD1$Trait <- ("E2PGD1")
out.cimE2PGD2 <- cim(data_2, pheno.col="E2D2",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD2$Trait <- ("E2PGD2")
out.cimE2PGD3 <- cim(data_2, pheno.col="E2D3",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD3$Trait <- ("E2PGD3")
out.cimE2PGD4 <- cim(data_2, pheno.col="E2D4",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD4$Trait <- ("E2PGD4")
out.cimE2PGD5 <- cim(data_2, pheno.col="E2D5",map.function=c("kosambi"),method=c("hk"))
out.cimE2PGD5$Trait <- ("E2PGD5")
out.cimE2GIavg <- cim(data_2, pheno.col="E2GI",map.function=c("kosambi"),method=c("hk"))
out.cimE2GIavg$Trait <- ("E2GIavg")
out.cimE3PGD1 <- cim(data_2, pheno.col="E3D1",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD1$Trait <- ("E3PGD1")
out.cimE3PGD2 <- cim(data_2, pheno.col="E3D2",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD2$Trait <- ("E3PGD2")
out.cimE3PGD3 <- cim(data_2, pheno.col="E3D3",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD3$Trait <- ("E3PGD3")
out.cimE3PGD4 <- cim(data_2, pheno.col="E3D4",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD4$Trait <- ("E3PGD4")
out.cimE3PGD5 <- cim(data_2, pheno.col="E3D5",map.function=c("kosambi"),method=c("hk"))
out.cimE3PGD5$Trait <- ("E3PGD5")
out.cimE3GIavg <- cim(data_2, pheno.col="E3GI",map.function=c("kosambi"),method=c("hk"))
out.cimE3GIavg$Trait <- ("E3GIavg")

QTL.LZ8.ERA8 <- rbind(out.cimE1PGD1, out.cimE1PGD2, out.cimE1PGD3, out.cimE1PGD4, out.cimE1PGD5, out.cimE1GIavg, out.cimE2PGD1, out.cimE2PGD2, out.cimE2PGD3, out.cimE2PGD4, out.cimE2PGD5, out.cimE2GIavg,out.cimE3PGD1, out.cimE3PGD2, out.cimE3PGD3, out.cimE3PGD4, out.cimE3PGD5, out.cimE3GIavg)
# write.table(QTL.LZ8.ERA8, "./QTLLZ8All.txt", sep="\t")
```

```{r eval=FALSE}
a<-scanone(LZ8GBS, method="hk", pheno.col = "E1D1", n.perm=1000)
c<-scanone(LZ8GBS, method="hk", pheno.col = "E1D2", n.perm=1000)
d<-scanone(LZ8GBS, method="hk", pheno.col = "E1D3", n.perm=1000)
e<-scanone(LZ8GBS, method="hk", pheno.col = "E1D4", n.perm=1000)
f<-scanone(LZ8GBS, method="hk", pheno.col = "E1D5", n.perm=1000)
g<-scanone(LZ8GBS, method="hk", pheno.col = "E1GI", n.perm=1000)
b1<-scanone(LZ8GBS, method="hk", pheno.col = "E2D1", n.perm=1000)
c1<-scanone(LZ8GBS, method="hk", pheno.col = "E2D2", n.perm=1000)
d1<-scanone(LZ8GBS, method="hk", pheno.col = "E2D3", n.perm=1000)
e1<-scanone(LZ8GBS, method="hk", pheno.col = "E2D4", n.perm=1000)
f1<-scanone(LZ8GBS, method="hk", pheno.col = "E2D5", n.perm=1000)
g1<-scanone(LZ8GBS, method="hk", pheno.col = "E2GI", n.perm=1000)
h<-scanone(LZ8GBS, method="hk", pheno.col = "E3D1", n.perm=1000)
i<-scanone(LZ8GBS, method="hk", pheno.col = "E3D2", n.perm=1000)
j<-scanone(LZ8GBS, method="hk", pheno.col = "E3D3", n.perm=1000)
k<-scanone(LZ8GBS, method="hk", pheno.col = "E3D4", n.perm=1000)
l<-scanone(LZ8GBS, method="hk", pheno.col = "E3D5", n.perm=1000)
m<-scanone(LZ8GBS, method="hk", pheno.col = "E3GI", n.perm=1000)
summary(a) #
summary(c) #
summary(d) #
summary(e) #
summary(f) #
summary(g) #
summary(b1) #
summary(c1) #
summary(d1) #
summary(e1) #
summary(f1) #
summary(g1) #
summary(h) #
summary(i) #
summary(j) #
summary(k) #
summary(l) #
summary(m) #
```


For graphing purposes only, add a column to give unique positions for each marker per chromosome. 
```{r}
# uniqpos <- read.table("./GBS_UniquePos.txt",header=TRUE,na.string=c("", " ", "NA", "na"))
uniqpos$chr <- NULL
uniqpos$pos <- NULL
QTL.LZ8.ERA8 <- as.data.frame(QTL.LZ8.ERA8)
LZ8  <- cbind(QTL.LZ8.ERA8, uniqpos)
```


QTL Graph 
```{r  warning=FALSE, message=FALSE}
ggplot(LZ8, aes(x=LZ8$order, y=LZ8$lod))+
  geom_point(aes(colour = factor(Genome)),size = 2)+ylim(0,6)+theme_bw()+ theme(axis.text = font,  axis.title = font, axis.text.x=element_blank())+ scale_color_manual(values=c("#0A0A0A", "#8A8A8A", "#D1D1D1","#A2CD5A"))+ 
  labs(x = "Chromosome 1A - 7D and Unknown" , y = "LOD", title="ABA Sensitivity QTL")
```


### Heading and Height  

QTL Analysis
```{r  warning= FALSE, message=FALSE}
data_2 <- calc.genoprob(LZ8GBS, step=0)
out.cimHeight <- cim(data_2, pheno.col="Height",map.function=c("kosambi"),method=c("hk"))
out.cimHeight$Trait <- ("Height") 
out.cimHeading <- cim(data_2, pheno.col="Heading",map.function=c("kosambi"),method=c("hk"))
out.cimHeading$Trait <- ("Heading")
```

Calculate Significance Threshold
```{r eval=FALSE}
a<-scanone(LZ8GBS, method="hk", pheno.col = "Heading", n.perm=1000)
summary(a) #4.43 5%
b<-scanone(LZ8GBS, method="hk", pheno.col = "Height", n.perm=1000)
summary(b) #4.38 5%
```

Graph the Manhatten Plot
```{r  warning= FALSE, message=FALSE}
QTL.LZ8.ERA8 <- as.data.frame(out.cimHeading)
QTLheadingLZ8  <- cbind(QTL.LZ8.ERA8, uniqpos)

ggplot(QTLheadingLZ8, aes(x=QTLheadingLZ8$order, y=QTLheadingLZ8$lod))+
  geom_point(aes(colour = factor(Genome)), size = 2)+theme_bw()+ylim(0,6)+ 
  theme(axis.text = font,  axis.title = font, axis.text.x=element_blank())+ 
  scale_color_manual(values=c("#0A0A0A", "#8A8A8A", "#D1D1D1","#A2CD5A"))+ geom_hline(aes(yintercept = 4.4))+ 
  labs(x = "Chromosome 1A - 7D and Unknown" , y = "LOD", title="Heading Date QTL")

QTL.LZ8.ERA8 <- as.data.frame(out.cimHeight)
QTLheightLZ8  <- cbind(QTL.LZ8.ERA8, uniqpos)

ggplot(QTLheightLZ8, aes(x=QTLheightLZ8$order, y=QTLheightLZ8$lod))+
  geom_point(aes(colour = factor(Genome)), size = 2)+theme_bw()+ylim(0,6) +
  theme(axis.text = font,  axis.title = font, axis.text.x=element_blank())+ 
  scale_color_manual(values=c("#0A0A0A", "#8A8A8A", "#D1D1D1","#A2CD5A"))+ geom_hline(aes(yintercept = 4.4))+ 
  labs(x = "Chromosome 1A - 7D and Unknown" , y = "LOD", title="Height QTL")


# uniqposAHH <- read.table("./GBS_UniquePos_ABAHeadHei.txt",header=TRUE,na.string=c("", " ", "NA", "na"))
uniqposAHH$chr <- NULL
uniqposAHH$pos <- NULL
QTL.LZ8.ERA8 <- rbind(out.cimE1PGD1, out.cimE1PGD2, out.cimE1PGD3, out.cimE1PGD4, 
                      out.cimE1PGD5, out.cimE1GIavg, out.cimE2PGD1, out.cimE2PGD2, 
                      out.cimE2PGD3, out.cimE2PGD4, out.cimE2PGD5, out.cimE2GIavg,
                      out.cimE3PGD1, out.cimE3PGD2, out.cimE3PGD3, out.cimE3PGD4, 
                      out.cimE3PGD5, out.cimE3GIavg, out.cimHeight, out.cimHeading )
QTL.LZ8.ERA8 <- as.data.frame(QTL.LZ8.ERA8)
QTL.LZ8  <- cbind(QTL.LZ8.ERA8, uniqposAHH)
ggplot(QTL.LZ8, aes(x=QTL.LZ8$order, y=QTL.LZ8$lod))+
  geom_point(aes(colour = factor(Genome)),size = 2)+ylim(0,6)+theme_bw()+ 
  theme(axis.text = font,  axis.title = font, axis.text.x=element_blank())+ 
  scale_color_manual(values=c("#0A0A0A", "#8A8A8A", "#D1D1D1","#A2CD5A")) + geom_hline(aes(yintercept = 4.4))+ 
  labs(x = "Chromosome 1A - 7D and Unknown" , y = "LOD", title="ABA, Heading Date, and Height QTL")

QTL.LZ8.4A <-  subset(QTL.LZ8 ,  QTL.LZ8$chr=="4A.1" | QTL.LZ8$chr=="4A.2" | QTL.LZ8$chr=="4A.3" )
ggplot(QTL.LZ8.4A, aes(x=QTL.LZ8.4A$order, y=QTL.LZ8.4A$lod))+
  geom_point(aes(colour = factor(chr)),size = 2)+ylim(0,6)+theme_bw()+ 
  theme(axis.text = font,  axis.title = font, axis.text.x=element_blank())+ 
  scale_color_manual(values=c("#0A0A0A", "#8A8A8A", "#D1D1D1")) + geom_hline(aes(yintercept = 4.4))+ 
  labs(x = "Chromosome 4A" , y = "LOD", title="ABA, Heading Date, and Height QTL")

```

List of Significant QTL on Chromosome 4A 
```{r  warning = FALSE, message=FALSE}
QTL.LZ8.4A %>% 
  mutate(lod = round(lod,2)) %>%
  filter(lod > 4.4) %>%
  arrange(str_extract(chr, '^.'), pos) %>%
  dplyr::select(Marker, chr, pos,  Trait, lod)  %>%
  kable(caption = "Table 1: Summary of QTL with a LOD > 4.4 on Chromosome 4A") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) 
```

## Otis/ZakERA8 F2:3 

The `OZ8` dataset contains the Otis/ZakERA8 F2: F3 genotypic data, phenotypic data, and marker positions on chromosome 4A.  
```{r eval = FALSE}
OZ8<-read.cross("csv",".","./OZ8_SNP6-SNP29.csv",na.strings=c("-","NA","."),BC.gen=0, F.gen=2)
```
```{r warning = FALSE, message=FALSE}
OZ8
# geno.image(OZ8)
# summary(OZ8$pheno)
```

**Check for skewed markers**  
```{r}
gt<-geno.table(OZ8)
gt[gt$P.value<0.05/totmar(OZ8),]  
```
No markers are skewed.  
</br>
The phenotypes include percent germination (`PG`) is separated by day (d1...d5) and Germination Index (`GI`) is calculated over all 5 days:  
> PG_d1, 	PG_d2,	PG_d3,	PG_d4,	PG_d5,	GI  

#### Compite Interval Mapping
```{r eval = FALSE}
data_2 <- calc.genoprob(OZ8, step=0)
out.cimGI <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
a<-scanone(OZ8, method="hk", pheno.col = "GI", n.perm=1000)
summary(a) 

out.cimd5 <- cim(data_2, pheno.col="PG_d5",map.function=c("kosambi"),method=c("hk"))
out.cimd4 <- cim(data_2, pheno.col="PG_d4",map.function=c("kosambi"),method=c("hk"))
out.cimd3 <- cim(data_2, pheno.col="PG_d3",map.function=c("kosambi"),method=c("hk"))
out.cimd2 <- cim(data_2, pheno.col="PG_d2",map.function=c("kosambi"),method=c("hk"))
out.cimd1 <- cim(data_2, pheno.col="PG_d1",map.function=c("kosambi"),method=c("hk"))
```

```{r echo = FALSE}
data_2 <- calc.genoprob(OZ8, step=0)
out.cimGI <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))
out.cimd5 <- cim(data_2, pheno.col="PG_d5",map.function=c("kosambi"),method=c("hk"))
out.cimd4 <- cim(data_2, pheno.col="PG_d4",map.function=c("kosambi"),method=c("hk"))
out.cimd3 <- cim(data_2, pheno.col="PG_d3",map.function=c("kosambi"),method=c("hk"))
out.cimd2 <- cim(data_2, pheno.col="PG_d2",map.function=c("kosambi"),method=c("hk"))
out.cimd1 <- cim(data_2, pheno.col="PG_d1",map.function=c("kosambi"),method=c("hk"))
```

#### Wrangle Results
```{r}
out.cimd5$Pheno <- "d5"
out.cimd4$Pheno <- "d4"
out.cimd3$Pheno <- "d3"
out.cimd2$Pheno <- "d2"
out.cimd1$Pheno <- "d1"
out.cimGI$Pheno <- "GI"
Otera8 <- rbind(out.cimGI ,out.cimd5,out.cimd4,out.cimd3,out.cimd2,out.cimd1 )
```

```{r echo = FALSE}
data_2 <- calc.genoprob(OZ8, step=0)
out.cimGI <- cim(data_2, pheno.col="GI",map.function=c("kosambi"),method=c("hk"))

out.cimd5 <- cim(data_2, pheno.col="PG_d5",map.function=c("kosambi"),method=c("hk"))

out.cimd4 <- cim(data_2, pheno.col="PG_d4",map.function=c("kosambi"),method=c("hk"))
out.cimd3 <- cim(data_2, pheno.col="PG_d3",map.function=c("kosambi"),method=c("hk"))
out.cimd2 <- cim(data_2, pheno.col="PG_d2",map.function=c("kosambi"),method=c("hk"))
out.cimd1 <- cim(data_2, pheno.col="PG_d1",map.function=c("kosambi"),method=c("hk"))

out.cimd5$Pheno <- "d5"
out.cimd4$Pheno <- "d4"
out.cimd3$Pheno <- "d3"
out.cimd2$Pheno <- "d2"
out.cimd1$Pheno <-"d1"
out.cimGI$Pheno <-"GI"
Otera8 <- rbind(out.cimGI ,out.cimd5,out.cimd4,out.cimd3,out.cimd2,out.cimd1 )
```

#### Graph Results 
```{r warning = FALSE, message=FALSE}
ggplot(Otera8, aes(x=Otera8$pos, y=Otera8$lod, colour = factor(Otera8$Pheno)))+
  geom_line(size = 1.5)+
  theme_bw()+ theme(axis.text = font,  axis.title = font)+
  geom_hline(aes(yintercept = 1.73, colour = ""))+ 
  labs(x = "Chromosome 4A (cM)", y = "LOD") 
```

```{r eval = FALSE}
out.cimGI2 <- rbind(out.cimGI, out.cimd5)
ggplot(out.cimGI2, aes(x=out.cimGI2$pos, y=out.cimGI2$lod))+
  geom_line(aes(colour = factor(Pheno)),size = 1)+
  theme_bw()+ theme(axis.text = font,  axis.title = font)+
  geom_hline(aes(yintercept = 1.78))+ 
  labs(x = "Chromosome 4A (cM)", y = "LOD")  +
  ylim (0,10) +xlim (0,11)+
  scale_color_manual(values=c("#CD6600","#FFB90F")) #+ theme(legend.position="none")
```

## Figure 3c
```{r echo = FALSE}
out.cimGI2 <- rbind(out.cimGI, out.cimd5)
ggplot(out.cimGI2, aes(x=out.cimGI2$pos, y=out.cimGI2$lod))+
  geom_line(aes(colour = factor(Pheno)),size = 1)+
  theme_bw()+ theme(axis.text = font,  axis.title = font)+
  geom_hline(aes(yintercept = 1.78))+ 
  labs(x = "Chromosome 4A (cM)", y = "LOD")  +
  ylim (0,10) +xlim (0,11)+
  scale_color_manual(values=c("#CD6600","#FFB90F")) #+ theme(legend.position="none")
```
